---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# osmextract.tools

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- [![CRAN status](https://www.r-pkg.org/badges/version/osmextract.tools)](https://CRAN.R-project.org/package=osmextract.tools) -->
<!-- badges: end -->

The goal of osmextract.tools is to provide additional functionalities for the data obtained with `osmextract`.

:::{.callout-warning}
This package is under active development and may change without notice.
:::

## Installation

You can install the development version of osmextract.tools from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("juanfonsecaLS1/osmextract.tools")
```

## Example

A common use of OSM data is to prepare routable networks. The following example shows how to use `osmextract.tools` to prepare a routable network from OSM data.

The following code will download OSM data for a given area, extract the road network, and return a `sfnetwork` object representing a directed graph.

```{r} 
#| label: example
#| eval: false

library(osmextract.tools)
library(sf)

## basic example code

my_area <- sf::st_point(c(-1.5584637048901326, 53.80817188808102)) |>
  sf::st_sfc(crs = 4326) |>
  sf::st_buffer(units::set_units(1, "km"))

sfnet <- oe_get_sfnetwork(my_area, "driving", directed = TRUE)
```

```{r}
#| label: example1-code
#| echo: false

devtools::load_all()

my_area <- sf::st_point(c(-1.5584637048901326, 53.80817188808102)) |>
  sf::st_sfc(crs = 4326) |>
  sf::st_buffer(units::set_units(1, "km"))

sfnet <- oe_get_sfnetwork(my_area, "driving", directed = TRUE)
```

A quick visualisation
```{r}
#| label: example1-plot
plot(sfnet)
```